\chapter{Abstract}
<<<<<<< HEAD
This report describes the 4th semester project E4PRJ4 at Aarhus School of Engineering. The study deals with three major systems; a dynanometer named Rolling Road, the electrical systems of Aarhus University's vehicle dubbed AU2 and an user interface called Rolling Road GUI. The main goal of the project is to complete and prepare the systems to take part in the Shell Eco-Marathon, an international competition pertaining to the submission of the most fuel efficient vehicles. Nonetheless, in the documentation each of the systems are comprehensively described in detail. This includes, however, is not limited to the systems' documentations of software and hardware. Furthermore, the working process has also been addressed from beginning to end \fxnote{Omformuler - TN}. \\
=======
This study describes the 4\textsuperscript{th} term semester project E4PRJ4 at Aarhus School of Engineering. The study\fxnote{study?} deals with three major systems; a dynanometer named Rolling Road, the electrical systems of Aarhus University's vehicle dubbed AU2 and an user interface called Rolling Road GUI. The main goal of the project is to complete and prepare the systems in order to participate in the Shell Eco-Marathon 2016 - an international competition pertaining to the submission of the most fuel efficient vehicles. Nonetheless, in the study \fxnote{Hvilket study, er det doku eller rapport? TN} each of the systems are comprehensively described in detail. This includes, however, is not limited to the systems' documentations of  software and hardware. Furthermore, the working process has also been addressed from beginning to end \fxnote{Omformuler - TN}. \\
>>>>>>> origin/master
AU2 contains a vast variety of capabilities and can among other things utilize lithium polymer batteries to power the complex systems contained in AU2.
Protection of the batteries is enforced with a Battery Management System. Furthermore, a highly energy-efficient driving algorithm is used to ensure optimal driving operation, which is enforced by the Motor Control System. Data can also be logged to be analysed after a run on a track.
The Rolling Road and the Rolling Road GUI can be used together or separately to test the efficiency of the drive line/drive train of AU2 and optimize it for a given run or track. The GUI offers a real time overview of the test results from Rolling Road simulations.\\

The development process is completed with the use of an suitable adaptation of SCRUM, where each week consisted among other things of sprint coordination, stand-up - and consultant meetings. This tool have proved as a great
supplementary help in completing the study \fxnote{Gør det her afsnit kortere - TN}.\\
The Rolling Road and Rolling Road GUI are both implemented and working, however, some parts of AU2 are not fully functioning yet. \\

In the end a polished and well-done documentation appeared.