\section{Functional Requirement Rolling Road}

\begin{enumerate}
	\item Rolling Road.
	\begin{enumerate}
		\item force application.
		\begin{enumerate}
			\item Rolling Road must be able to hold a constant force on the subject.
		\end{enumerate}
		\item changing force on the subject.
		\begin{enumerate}
			\item Control-panel can change the force that is delivered to the subject.
			\item PID control force application though power circuit.
			\begin{enumerate}
				\item PID constants can be change from the Control-panel.
				\item Anti windup.
			\end{enumerate}
		\end{enumerate}
		\item safety.
		\begin{enumerate}
			\item Rolling Road must turn off if the "load circuit" exceed 16 Amps.
		\end{enumerate}
		\item Measurement.
		\begin{enumerate}
			\item Current monitoring of the generator.
			\item Power measurement on the engine in the Subject.
			\item Force and Speed measurement of the Subject to calculate the power.
			\item Time.
			\item Calculate the power.
		\end{enumerate}
		\item Calibrate
		\begin{enumerate}
			\item Control-panel can adjust the Rolling Roads sensor, set them all to zero.
		\end{enumerate}
		\item Communication
		\begin{enumerate}
			\item Serial UART connection between the Control-panel and the Rolling Road. See the protocol. 
		\end{enumerate}
	\end{enumerate}
	\item Sensors
	\begin{enumerate}
		\item HAL sensor.
		\begin{enumerate}
			\item To measure the current thought the generator and electric motor in the subject.
		\end{enumerate}
		\item Voltage sensor.
		\begin{enumerate}
			\item To measure the potential over the electric motor in the subject.    
		\end{enumerate}
		\item Moment transducer.
		\begin{enumerate}
			\item to measure the moment from the force application.
			\item Can also measure speed.
		\end{enumerate}
	\end{enumerate}
	\item Actuator
	\begin{enumerate}
		\item Power Circuit.
		\begin{enumerate}
			\item Can be control with a PWM signal from the micro processor.
			\begin{enumerate}
				\item Micro processor use a PID regulator to control the PWM signal.
			\end{enumerate}
			\item It is use to control the force application.
		\end{enumerate}
	\end{enumerate}
	\item Memory
	\begin{enumerate}
		\item Use an EEPROM to save all impotent data.
		\begin{enumerate}
			\item Offset values to all sensors.
			\item PID constants.
			\item Wanted force effects on the subject.
		\end{enumerate}
	\end{enumerate} 
\end{enumerate}
